\chapter*{References}
\addcontentsline{toc}{chapter}{References}
\thispagestyle{plain}

\begin{thebibliography}{99}
\setlength{\itemsep}{4pt}

\bibitem{rfb} T. Richardson and J. Levine, \emph{The Remote Framebuffer
Protocol}, RFC 6143, Internet Engineering Task Force, March 2011.

\bibitem{vnc} T. Richardson, Q. Stafford-Fraser, K. R. Wood, and A. Hopper,
``Virtual Network Computing,'' \emph{IEEE Internet Computing}, vol. 2, no. 1,
pp. 33--38, 1998.

\bibitem{rdp} Microsoft Corporation, \emph{[MS-RDPBCGR]: Remote Desktop Protocol
--- Basic Connectivity and Graphics Remoting}, Microsoft Open Specifications,
2023.

\bibitem{webrtc} H. Alvestrand, ``Overview: Real-Time Protocols for
Browser-Based Applications,'' RFC 8825, Internet Engineering Task Force, January
2021.

\bibitem{ice} A. Keranen, C. Holmberg, and J. Rosenberg, ``Interactive
Connectivity Establishment (ICE): A Protocol for Network Address Translator
(NAT) Traversal,'' RFC 8445, Internet Engineering Task Force, July 2018.

\bibitem{stun} M. Petit-Huguenin, G. Salgueiro, J. Rosenberg, D. Wing, R. Mahy,
and P. Matthews, ``Session Traversal Utilities for NAT (STUN),'' RFC 8489,
Internet Engineering Task Force, February 2020.

\bibitem{turn} T. Reddy, A. Johnston, P. Matthews, and J. Rosenberg,
``Traversal Using Relays around NAT (TURN),'' RFC 8656, Internet Engineering
Task Force, February 2020.

\bibitem{dtls} E. Rescorla and N. Modadugu, ``Datagram Transport Layer Security
Version 1.2,'' RFC 6347, Internet Engineering Task Force, January 2012.

\bibitem{srtp} M. Baugher, D. McGrew, M. Naslund, E. Carrara, and K. Norrman,
``The Secure Real-time Transport Protocol (SRTP),'' RFC 3711, Internet
Engineering Task Force, March 2004.

\bibitem{ed25519} S. Josefsson and I. Liusvaara, ``Edwards-Curve Digital
Signature Algorithm (EdDSA),'' RFC 8032, Internet Engineering Task Force,
January 2017.

\bibitem{h264} ITU-T, \emph{Recommendation H.264: Advanced Video Coding for
Generic Audiovisual Services}, International Telecommunication Union, 2021.

\bibitem{rust} S. Klabnik and C. Nichols, \emph{The Rust Programming Language},
2nd ed. San Francisco, CA: No Starch Press, 2023.

\bibitem{tokio} Tokio Contributors, ``Tokio: An Asynchronous Runtime for the
Rust Programming Language,'' \url{https://tokio.rs}, accessed 2026.

\bibitem{webrtcrs} WebRTC.rs Contributors, ``webrtc-rs: A Pure Rust
Implementation of WebRTC,'' \url{https://github.com/webrtc-rs/webrtc}, accessed
2026.

\bibitem{tauri} Tauri Contributors, ``Tauri: Build Smaller, Faster, and More
Secure Desktop Applications,'' \url{https://tauri.app}, accessed 2026.

\bibitem{rustdesk} RustDesk Contributors, ``RustDesk: An Open-Source Remote
Desktop Application,'' \url{https://github.com/rustdesk/rustdesk}, accessed 2026.

\bibitem{ddapi} Microsoft Corporation, ``Desktop Duplication API,'' Windows
Developer Documentation, accessed 2026.

\bibitem{openh264} Cisco Systems, ``OpenH264: An Open-Source H.264 Codec,''
\url{https://github.com/cisco/openh264}, accessed 2026.

\end{thebibliography}
